\textbf{Emergency Service Location Optimization in a Multi-Zone District based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
error fixing

Under the given conditions, we can easily find the optimal ambulance placement using a brute force
method: trying all $\binom{6}{3}$ choices of ambulance placements, and picking the one with the highest total coverage.
However, this solution is not scalable to larger cities, as the brute force method has time complexity
$O(n) = nk\binom{n}{k}$ where $n$ is the number of zones to cover, and $k$ is the number of ambulances to place, which
becomes intractable as $n$ and $k$ increase (since it has to check $\binom{n}{k}$ placements,
and calculating the total coverage of each placement requires $nk$ computations, summing the $k$ zone-zone
coverages for each of the $n$ ambulances). Quadrupling the size of the city
increases the computations required by a factor of 2 million (assuming the average zone size stays the same,
and the number of ambulances increases proportionally).

Therefore, a more scalable solution is needed. We discovered that a greedy heuristic also gives a good solution,
except with a much lower time complexity of $O(n) = n^2k$.

@@

\subsection{Dynamic Approach}
With only a total of six zones and a maximum of $n = 3$ ambulances to allocate, overall algorithm efficiency is not a pressing issue. As we have shown above, even a brute force attempt at optimizing the ambulance locations takes a negligent amount of time. However, as we look to expanding the model to fit a larger area, with more zones, and more ambulances, it becomes increasingly more important to look for ways to make our algorithm more efficient.

Even after our greedy algorithm reduces the overall solution time to an $O(n) = n^2k$, or polynomial time, there are still possible ways to improve it. One such method would be the use of dynamic programming methods to split the problem up into a series of smaller subproblems, and then merge the results together. As a result of such a method, we would reduce the problem to one with an $O(n) = nlog(n)$, an algorithm that would easily scale to larger data sets.

@@

\item Allocate $n$ ambulances across each subdistrict. If there are fewer ambulances than are necessary to cover the entire district, weight each subdistrict by population size (save more people per ambulance)

\item Solve each subdistrict for the optimal ambulance location, thereby finding a solution for the set as a whole
\end{enumerate}

>>>>

Under the given conditions, we can easily find the optimal ambulance placement using a brute force
method: trying all $\binom{6}{3}$ choices of ambulance placements, and picking the one with the highest total coverage.
However, this solution is not scalable to larger cities, as the brute force method has time complexity
$O(n, k) = nk\binom{k}{n}$ where $k$ is the number of zones to cover, and $n$ is the number of ambulances to place, which
becomes intractable as $n$ and $k$ increase (since it has to check $\binom{k}{n}$ placements,
and calculating the total coverage of each placement requires $nk$ computations, summing the $k$ zone-zone
coverages for each of the $n$ ambulances). Quadrupling the size of the city
increases the computations required by a factor of 2 million (assuming the average zone size stays the same,
and the number of ambulances increases proportionally).

Therefore, a more scalable solution is needed. We discovered that a greedy heuristic also gives a good solution,
except with a much lower time complexity of $O(n, k) = n k^2$.

@@

\subsection{Dynamic Approach}
With only a total of six zones and a maximum of $n = 3$ ambulances to allocate, overall algorithm efficiency is not a pressing issue. As we have shown above, even a brute force attempt at optimizing the ambulance locations takes a negligible amount of time. However, as we look to expanding the model to fit a larger area, with more zones, and more ambulances, it becomes increasingly more important to look for ways to make our algorithm more efficient.

Even after our greedy algorithm reduces the overall solution time to an $O(n, k) = nk^2$, or polynomial time, there are still possible ways to improve it. One such method would be the use of dynamic programming methods to split the problem up into a series of smaller subproblems, and then merge the results together. As a result of such a method, we would reduce the problem to one with an $O(n, k) = nk\log(k)$, an algorithm that would easily scale to larger data sets.

@@

\item Allocate $n$ ambulances across the subdistricts. If there are fewer ambulances than are necessary to cover the entire district, weight each subdistrict by population size (save more people per ambulance).

\item Solve each subdistrict for the optimal ambulance location, thereby finding a solution for the set as a whole.
\end{enumerate}
